### 2021-05-20 README.Rmd
correct https URLs
adjust site url syntax
remove redundant horizontal line
github md style automatically draws a horizontal line after level 1 headers

# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=250 />

@@

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://https://infer.tidymodels.org/>.

>>>>

# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=280 />

@@

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
